### 2015-09-05 463assignment/463assignment_takei.tex

Due to the fact that there are so many OR genes in the human genome, and that these ORs work in a combinatorial manner, it has been difficult for the researchers to decipher the complete code of olfaction \citep{Hasin-Brumshtein2009, Nei2008}.
In addition to this, ORs are highly copy number variable within and between species, adding greater complexity to the olfactory process which remains to be a challenge for the researchers to make a connection between OR CNV with the phenotype \citep{Nozawa2007}.

OR genes also have an important implications in the evolution of different species.
Two major classes of OR genes have been identified: class I and class II genes, or ``fish-like'' and ``mammalian-like'' genes respectively, as the different classes of genes were found mainly in their respective species \citep{Glusman2000}.
The study by \citet{Niimura2005} showed that the diversity of the OR gene families in fishes was greater than that of the mammalian OR gene families, even though the number of OR genes in a single family were less in fishes.
Furthermore, they showed that amphibians have retained the diversity of the gene families as the fishes, while also having the large repertoire of OR genes in one family as in the mammals, signifying the fact that the CNV was likely due to the adaptation process from being aquatic to terrestial \citep{Niimura2005}.

>>>>

Due to the fact that there are so many OR genes in the human genome, and that these ORs work in a combinatorial manner, it has been difficult for researchers to decipher the complete code of olfaction \citep{Hasin-Brumshtein2009, Nei2008}.
In addition to this, ORs are highly copy number variable within and between species, adding greater complexity to the olfactory process which remains to be a challenge for the researchers to make a connection between OR CNV and phenotype \citep{Nozawa2007}.

OR genes also have important implications in the evolution of different species.
Two major classes of OR genes have been identified: class I and class II genes, or ``fish-like'' and ``mammalian-like'' genes respectively, as the different classes of genes were found mainly in their respective species \citep{Glusman2000}.
The study by \citet{Niimura2005} showed that the diversity of the OR gene families in fish was greater than that of the mammalian OR gene families, even though the number of OR genes in a single family were less in fish.
Furthermore, they showed that amphibians have retained the same diversity of the gene families as the fish, while also having as large a repertoire of OR genes in one family as in the mammals, signifying the fact that the CNV was likely due to the adaptation process in the transition from being aquatic to terrestial \citep{Niimura2005}.
